Improvement of crash forces in structures using optimization tools.

### 2016-07-28 paper.tex
Minor

Firstly, with the parametrized model, a sampling of !!N!! samples is performed, relying on the LHS technique. This method creates a set of data with homogeneous projections on each variable axis, so that no superimposed projections appear.

@@

Furthermore, other researchers have traditionally swerved towards optimization of the specific energy absorption (SEA) and the load ratio (LR) \cite{Hou2007555}. Thus, they were also evaluated as objective functions, but it was found that during the optimization process these quantities have a more complicated comportment and a noisier nature for this model.

>>>>

Firstly, with the parametrized model, a sampling of $n$ samples is performed, relying on the LHS technique. This method creates a set of data with homogeneous projections on each variable axis, so that no superimposed projections appear.

@@

Furthermore, other researchers have traditionally swerved towards optimization of the specific energy absorption (SEA) and the load ratio (LR) \cite{Hou2007555}. Thus, they are also evaluated as objective functions, but considering their more complicated comportment and a noisier nature for this model.
